---
title: "Models For DREMT"
author: "Hannah Kimmel"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Library Loading
```{r setup, include=FALSE}
options(packrat.dependency.discovery.renv = TRUE)
require(ggplot2)
require(ggthemes)
require(plyr)
require(stargazer)
require(RColorBrewer)
require(scales)
require(gtable)
require(gridExtra)
require(data.table)
require(dplyr)
require(ggplot2)
require(readr)
require(tidyr)
require(lme4)
require(MASS)
library(daewr)
library(MASS)
library(GAD)
library(dplyr)
library(sjPlot)
library(blmeco)
```

## Models

Low dispersion! Can be used to estimate/predict responses
```{r}
library(lme4)
library(GAD)
library(blmeco)
DMSOdsewithrep <- subset(dswithrep, Metadata_Treatment == "DMSO")

DMSOdsewithrep$CollagenI <- relevel(factor(DMSOdsewithrep$CollagenI, levels = c(0,0.25,0.5,0.75,1)), ref = 5)
DMSOdsewithrep$CollagenIV <- relevel(factor(DMSOdsewithrep$CollagenIV, levels = c(0,0.25,0.5,0.75,1)), ref = 5)
DMSOdsewithrep$Laminin <- relevel(factor(DMSOdsewithrep$Laminin, levels = c(0,0.25,0.5,0.75,1)), ref = 5)
DMSOdsewithrep$Hyaluronic_Acid <- relevel(factor(DMSOdsewithrep$Hyaluronic_Acid, levels = c(0,0.25,0.5,0.75,1)), ref = 5)
DMSOdsewithrep$TenascinC <- relevel(factor(DMSOdsewithrep$TenascinC, levels = c(0,0.25,0.5,0.75,1)), ref = 5)
DMSOdsewithrep$Osteopontin <- relevel(factor(DMSOdsewithrep$Osteopontin, levels = c(0,0.25,0.5,0.75,1)), ref = 5)
DMSOdsewithrep$Galectin3 <- relevel(factor(DMSOdsewithrep$Galectin3, levels = c(0,0.25,0.5,0.75,1)), ref = 5)
DMSOdsewithrep$Fibronectin <- relevel(factor(DMSOdsewithrep$Fibronectin, levels = c(0,0.25,0.5,0.75,1)), ref = 5)
DMSOdsewithrep$Decorin <- relevel(factor(DMSOdsewithrep$Decorin, levels = c(0,0.25,0.5,0.75,1)), ref = 5)


vimmodel <- lmer(Mean_Orange_Norm ~ (1|Metadata_Stiffness:Metadata_Experiment:Metadata_Block:Replicate)+
                Metadata_Stiffness+ CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin + Abb_ECM + Metadata_Stiffness:(CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin)+ Metadata_Stiffness:Abb_ECM + Abb_ECM:(CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin) + Metadata_Stiffness:Abb_ECM:(CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin), data = DMSOdsewithrep)

ecadmodel <- lmer(Mean_Red_Norm ~ (1|Metadata_Stiffness:Metadata_Experiment:Metadata_Block:Replicate)+
                Metadata_Stiffness+ CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin + Abb_ECM + Metadata_Stiffness:(CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin)+ Metadata_Stiffness:Abb_ECM + Abb_ECM:(CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin) + Metadata_Stiffness:Abb_ECM:(CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin), data = DMSOdsewithrep)

pxrmodel <- lmer(Mean_Green_Norm ~ (1|Metadata_Stiffness:Metadata_Experiment:Metadata_Block:Replicate)+
                Metadata_Stiffness+ CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin + Abb_ECM + Metadata_Stiffness:(CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin)+ Metadata_Stiffness:Abb_ECM + Abb_ECM:(CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin) + Metadata_Stiffness:Abb_ECM:(CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin), data = DMSOdsewithrep)

dispersion_glmer(vimmodel)
dispersion_glmer(ecadmodel)
dispersion_glmer(pxrmodel)
```
## Summaries
```{r}
summary(vimmodel)
summary(ecadmodel)
summary(pxrmodel)

```
## Tab Models

```{r}

tab_model(vimmodel, ecadmodel, pxrmodel)
```


## Anovas
```{r}
vimanova <- anova(vimmodel)
ecadanova <- anova(ecadmodel)
pxranova <- anova(pxrmodel)
```

WP: 1 - pf(F-value, 1, 2)
SP: 1 -pf(F-value, df, 1167) (1167 = 1401 (total number of obs) - 1 - 233 (observed dfs))
```{r}
sum(vimanova$npar)

vimanova <- vimanova %>% mutate(p_value = ifelse(row.names(vimanova) == "Stiffness", 1 - pf(vimanova$`F value`, 1, 2), 1 - pf(vimanova$`F value`, vimanova$npar, 1167)))

ecadanova <- ecadanova %>% mutate(p_value = ifelse(row.names(ecadanova) == "Stiffness", 1 - pf(ecadanova$`F value`, 1, 2), 1 - pf(ecadanova$`F value`, ecadanova$npar, 1167)))

pxranova <- pxranova %>% mutate(p_value = ifelse(row.names(pxranova) == "Stiffness", 1 - pf(pxranova$`F value`, 1, 2), 1 - pf(pxranova$`F value`, pxranova$npar, 1167)))

vimanova <- vimanova %>% mutate(psig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      p_value > 0.05   ~ "",
      TRUE            ~ ""))

ecadanova <- ecadanova %>% mutate(psig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      p_value > 0.05   ~ "",
      TRUE            ~ ""))

pxranova <- pxranova %>% mutate(psig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      p_value > 0.05   ~ "",
      TRUE            ~ ""))
```
### Summary of Results
Key Takeaways: Stiffness is not a significant main factor and no significant 3-way interactions -> main factors still interpretable

Ratio: Vim is significantly impacted by ratio (all but C1,HA, DN), ECAD sig impacted by C1 and OPN Ratio, PXR by HA and LN
DN Ratio not sig for any

Abb_ECM is sig for all channels

Stiffness and Ratio Intx: PXR (C4, OPN, DN), ECAD (OPN, DN) Interesting to Note: Neither Stiffness nor Decorin Ratio were significant alone, but work synergistically (or antagonistically) in combination with each other

Stiffness and ECM: Not sig for any

Abb_ECM & Ratio: Vim significant for C1, C4, HA, FN, G3, while PXR only significant for G3

```{r}
vimpvalue <- vimanova[c("p_value", "psig")]
ecadpvalue <- ecadanova[c("p_value", "psig")]
pxrpvalue <- pxranova[c("p_value", "psig")]

colnames(vimpvalue) <- c("Vim p_value", "Vim psig")
colnames(ecadpvalue) <- c("Ecad p_value", "Ecad psig")
colnames(pxrpvalue) <- c("PXR p_value", "PXR psig")

anovaoverview <- cbind(vimpvalue, ecadpvalue, pxrpvalue)
write.csv(anovaoverview, "anovaoverview.csv")
```


### Visualization of Anova
```{r}
Anova_plot <- ggplot(data = vimanova,
                          aes(x = rownames(vimanova),
                              y = p_value)) +
  geom_bar(stat = "identity") + 
  geom_text(aes(x = rownames(vimanova), label = psig, y = 1),  
            size = 20, vjust = 0.8, nudge_y = 0.25) +
  # geom_errorbar(aes(ymin = Coefficient -
  #                     SE,
  #                   ymax = Coefficient +
  #                     SE, width = .1))+ 
theme(axis.title.x = element_text(size= 30),
      axis.text.x = element_text(size= 25),
      axis.title.y = element_text(size= 30),
      axis.text.y = element_text(size= 25),
      legend.text = element_text(size = 30),
      legend.title = element_text(size = 30),
      strip.text =  element_text(size = 30),
      panel.background = element_blank())+
  geom_bar(stat = "identity") + 
  xlab("Biomolecule combination") +
  ylab("ANOVA Coefficients for Vimentin") + 
 #  ylim(-0.5, 0.5)+
  coord_flip()
ggsave(filename = "anova_Vimentin.png", 
        width = 20, height = 15,units="in")

Regression_plot <- ggplot(data = ecadanova,
                          aes(x = rownames(ecadanova),
                              y = p_value)) +
  geom_bar(stat = "identity") + 
  geom_text(aes(x = rownames(ecadanova), label = psig, y = 0.65),  
            size = 20, vjust = 0.8, hjust = 0, nudge_y = 0.25) +
  # geom_errorbar(aes(x = reorder(Parameter, Coefficient),
  #                   ymin = Coefficient -
  #                     SE,
  #                   ymax = Coefficient +
  #                     SE, width = .1))+ 
theme(axis.title.x = element_text(size= 30),
      axis.text.x = element_text(size= 25),
      axis.title.y = element_text(size= 30),
      axis.text.y = element_text(size= 25),
      legend.text = element_text(size = 30),
      legend.title = element_text(size = 30),
      strip.text =  element_text(size = 30),
      panel.background = element_blank())+
  geom_bar(stat = "identity") + 
  xlab("Biomolecule combination") +
  ylab("ANOVA Coefficients for Ecad") + 
   #ylim(-0.5, 0.5)+
  coord_flip()
ggsave(filename = "anova_Ecad.png", 
        width = 20, height = 15,units="in")

Regression_plot <- ggplot(data = pxranova,
                          aes(x = rownames(pxranova),
                              y = p_value)) +
  geom_bar(stat = "identity") + 
  geom_text(aes(x = rownames(pxranova), label = psig, y = 0.65),  
            size = 20, vjust = 0.8, hjust = 0, nudge_y = 0.25) +
  # geom_errorbar(aes(x = reorder(Parameter, Coefficient),
  #                   ymin = Coefficient -
  #                     SE,
  #                   ymax = Coefficient +
  #                     SE, width = .1))+ 
theme(axis.title.x = element_text(size= 30),
      axis.text.x = element_text(size= 25),
      axis.title.y = element_text(size= 30),
      axis.text.y = element_text(size= 25),
      legend.text = element_text(size = 30),
      legend.title = element_text(size = 30),
      strip.text =  element_text(size = 30),
      panel.background = element_blank())+
  geom_bar(stat = "identity") + 
  xlab("Biomolecule combination") +
  ylab("ANOVA Coefficients for PXR") + 
  # ylim(-0.5, 0.5)+
  coord_flip()
ggsave(filename = "ANOVA_PXR.png", 
        width = 20, height = 15,units="in")
```


## ICCs
```{r}
library(performance)
icc(vimmodel)
icc(ecadmodel)
icc(pxrmodel)
```
## R2 Fit
```{r}
r2_nakagawa(vimmodel)
r2_nakagawa(ecadmodel)
r2_nakagawa(pxrmodel)
```
## Regression :)
### Setting up Tables

NOTE: This output of the model has the wrong df for stiffness, but even with the correct df, stiffness is not significant, so I didn't update it here
```{r}
library(parameters)

VimRegression <- as.data.frame(model_parameters(vimmodel))

EcadRegression <- as.data.frame(model_parameters(ecadmodel))

PXRRegression <- as.data.frame(model_parameters(pxrmodel))

VimRegression <- subset(VimRegression, Effects == "fixed")
EcadRegression <- subset(EcadRegression, Effects == "fixed")
PXRRegression <- subset(PXRRegression, Effects == "fixed")

VimRegression$Significance <- ""
EcadRegression$Significance <- ""
PXRRegression$Significance <- ""

VimRegression$Significance <- ifelse(VimRegression$p < 0.001, "***",
                                       ifelse(VimRegression$p < 0.01, "**",
                                              ifelse(VimRegression$p < 0.05, "*", "")))

EcadRegression$Significance <- ifelse(EcadRegression$p < 0.001, "***",
                                       ifelse(EcadRegression$p < 0.01, "**",
                                              ifelse(EcadRegression$p < 0.05, "*", "")))
PXRRegression$Significance <- ifelse(PXRRegression$p < 0.001, "***",
                                       ifelse(PXRRegression$p < 0.01, "**",
                                              ifelse(PXRRegression$p < 0.05, "*", "")))

VimRegressionSig <- subset(VimRegression, p < 0.05)
EcadRegressionSig <- subset(EcadRegression, p < 0.05)
PXRRegressionSig <- subset(PXRRegression, p < 0.05)
```

```{r}
VimRegressionSig$Parameter <- gsub("Abb_ECM", "", VimRegressionSig$Parameter) #remove Abb_ECMs
VimRegressionSig$Parameter <- gsub("^Metadata_Stiffness", "", VimRegressionSig$Parameter) #remove Metadata_Stiffness

EcadRegressionSig$Parameter <- gsub("Abb_ECM", "", EcadRegressionSig$Parameter) #remove Abb_ECMs
EcadRegressionSig$Parameter <- gsub("^Metadata_Stiffness", "", EcadRegressionSig$Parameter) #remove Metadata_Stiffness

PXRRegressionSig$Parameter <- gsub("Abb_ECM", "", PXRRegressionSig$Parameter) #remove Abb_ECMs
PXRRegressionSig$Parameter <- gsub("^Metadata_Stiffness", "", PXRRegressionSig$Parameter) #remove Metadata_Stiffness
```

```{r}
Regression_plot <- ggplot(data = VimRegressionSig,
                          aes(x = reorder(Parameter,Coefficient),
                              y = Coefficient)) +
  geom_bar(stat = "identity") + 
  geom_text(aes(x = reorder(Parameter,Coefficient), label = Significance, y = 0),  
            size = 20, vjust = 0.8, hjust = 0, nudge_y = 0.25) +
  geom_errorbar(aes(x = reorder(Parameter, Coefficient),
                    ymin = Coefficient -
                      SE,
                    ymax = Coefficient +
                      SE, width = .1))+ 
theme(axis.title.x = element_text(size= 30),
      axis.text.x = element_text(size= 25),
      axis.title.y = element_text(size= 30),
      axis.text.y = element_text(size= 25),
      legend.text = element_text(size = 30),
      legend.title = element_text(size = 30),
      strip.text =  element_text(size = 30),
      panel.background = element_blank())+
  geom_bar(stat = "identity") + 
  xlab("Biomolecule combination") +
  ylab("Linear Model Coefficients for Vimentin") + 
   ylim(-0.5, 0.5)+
  coord_flip()
ggsave(filename = "regression_Vimentin.png", 
        width = 15, height = 15,units="in")

Regression_plot <- ggplot(data = EcadRegressionSig,
                          aes(x = reorder(Parameter,Coefficient),
                              y = Coefficient)) +
  geom_bar(stat = "identity") + 
  geom_text(aes(x = reorder(Parameter,Coefficient), label = Significance, y = 0),  
            size = 20, vjust = 0.8, hjust = 0, nudge_y = 0.25) +
  geom_errorbar(aes(x = reorder(Parameter, Coefficient),
                    ymin = Coefficient -
                      SE,
                    ymax = Coefficient +
                      SE, width = .1))+ 
theme(axis.title.x = element_text(size= 30),
      axis.text.x = element_text(size= 25),
      axis.title.y = element_text(size= 30),
      axis.text.y = element_text(size= 25),
      legend.text = element_text(size = 30),
      legend.title = element_text(size = 30),
      strip.text =  element_text(size = 30),
      panel.background = element_blank())+
  geom_bar(stat = "identity") + 
  xlab("Biomolecule combination") +
  ylab("Linear Model Coefficients for Ecad") + 
   ylim(-0.5, 0.5)+
  coord_flip()
ggsave(filename = "regression_Ecad.png", 
        width = 15, height = 15,units="in")

Regression_plot <- ggplot(data = PXRRegressionSig,
                          aes(x = reorder(Parameter,Coefficient),
                              y = Coefficient)) +
  geom_bar(stat = "identity") + 
  geom_text(aes(x = reorder(Parameter,Coefficient), label = Significance, y = 0),  
            size = 20, vjust = 0.8, hjust = 0, nudge_y = 0.25) +
  geom_errorbar(aes(x = reorder(Parameter, Coefficient),
                    ymin = Coefficient -
                      SE,
                    ymax = Coefficient +
                      SE, width = .1))+ 
theme(axis.title.x = element_text(size= 30),
      axis.text.x = element_text(size= 25),
      axis.title.y = element_text(size= 30),
      axis.text.y = element_text(size= 25),
      legend.text = element_text(size = 30),
      legend.title = element_text(size = 30),
      strip.text =  element_text(size = 30),
      panel.background = element_blank())+
  geom_bar(stat = "identity") + 
  xlab("Biomolecule combination") +
  ylab("Linear Model Coefficients for PXR") + 
   ylim(-0.5, 0.5)+
  coord_flip()
ggsave(filename = "regression_PXR.png", 
        width = 15, height = 15,units="in")
```

### Shared Significant Factors/Intx Highlighted
Emphasizing the factors that are significant for all three phenotypes
```{r}
sharedpall <- c("LNDN" = "#DDA448", "25kPa:DNFN" = "#DDA448", "CollagenI0.5:C1FN" = "#DDA448", "Laminin0.5:LNG3" = "#DDA448")
```

```{r}
Regression_plot <- ggplot(data = VimRegressionSig,
                          aes(x = reorder(Parameter,Coefficient),
                              y = Coefficient, fill = Parameter)) +
  geom_bar(stat = "identity") + 
  geom_text(aes(x = reorder(Parameter,Coefficient), label = Significance, y = 0),  
            size = 20, vjust = 0.8, hjust = 0, nudge_y = 0.25) +
  scale_fill_manual(values = sharedpall) + 
  geom_errorbar(aes(x = reorder(Parameter, Coefficient),
                    ymin = Coefficient -
                      SE,
                    ymax = Coefficient +
                      SE, width = .1))+ 
theme(axis.title.x = element_text(size= 30),
      axis.text.x = element_text(size= 25),
      axis.title.y = element_text(size= 30),
      axis.text.y = element_text(size= 25),
      legend.text = element_text(size = 30),
      legend.title = element_text(size = 30),
      legend.position = "none", 
      strip.text =  element_text(size = 30),
      panel.background = element_blank())+
  geom_bar(stat = "identity") + 
  xlab("Biomolecule combination") +
  ylab("Linear Model Coefficients for Vimentin") + 
   ylim(-0.5, 0.5)+
  coord_flip()
ggsave(filename = "regression_VimentinShared.png", 
        width = 15, height = 15,units="in")

Regression_plot <- ggplot(data = EcadRegressionSig,
                          aes(x = reorder(Parameter,Coefficient),
                              y = Coefficient, fill = Parameter)) +
  geom_bar(stat = "identity") + 
  geom_text(aes(x = reorder(Parameter,Coefficient), label = Significance, y = 0),  
            size = 20, vjust = 0.8, hjust = 0, nudge_y = 0.25) +
  scale_fill_manual(values = sharedpall) +
  geom_errorbar(aes(x = reorder(Parameter, Coefficient),
                    ymin = Coefficient -
                      SE,
                    ymax = Coefficient +
                      SE, width = .1))+ 
theme(axis.title.x = element_text(size= 30),
      axis.text.x = element_text(size= 25),
      axis.title.y = element_text(size= 30),
      axis.text.y = element_text(size= 25),
      legend.text = element_text(size = 30),
      legend.title = element_text(size = 30),
      legend.position = "none", 
      strip.text =  element_text(size = 30),
      panel.background = element_blank())+
  geom_bar(stat = "identity") + 
  xlab("Biomolecule combination") +
  ylab("Linear Model Coefficients for Ecad") + 
   ylim(-0.5, 0.5)+
  coord_flip()
ggsave(filename = "regression_EcadShared.png", 
        width = 15, height = 15,units="in")

Regression_plot <- ggplot(data = PXRRegressionSig,
                          aes(x = reorder(Parameter,Coefficient),
                              y = Coefficient, fill = Parameter)) +
  geom_bar(stat = "identity") + 
  geom_text(aes(x = reorder(Parameter,Coefficient), label = Significance, y = 0),  
            size = 20, vjust = 0.8, hjust = 0, nudge_y = 0.25) +
  scale_fill_manual(values = sharedpall) +
  geom_errorbar(aes(x = reorder(Parameter, Coefficient),
                    ymin = Coefficient -
                      SE,
                    ymax = Coefficient +
                      SE, width = .1))+ 
theme(axis.title.x = element_text(size= 30),
      axis.text.x = element_text(size= 25),
      axis.title.y = element_text(size= 30),
      axis.text.y = element_text(size= 25),
      legend.text = element_text(size = 30),
      legend.title = element_text(size = 30),
      legend.position = "none", 
      strip.text =  element_text(size = 30),
      panel.background = element_blank())+
  geom_bar(stat = "identity") + 
  xlab("Biomolecule combination") +
  ylab("Linear Model Coefficients for PXR") + 
   ylim(-0.5, 0.5)+
  coord_flip()
ggsave(filename = "regression_PXRShared.png", 
        width = 15, height = 15,units="in")
```

## Testing: Do we need 3-way interactions?

Anovas say no... ICC goes slightly up (very slightly), dispersion stays the same, R2 goes down
```{r}
vimmodel2 <- lmer(Mean_Orange_Norm ~ (1|Metadata_Stiffness:Metadata_Experiment:Metadata_Block:Replicate)+
                Metadata_Stiffness+ CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin + Abb_ECM + Metadata_Stiffness:(CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin)+ Metadata_Stiffness:Abb_ECM + Abb_ECM:(CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin), data = DMSOdsewithrep)

pxrmodel2 <- lmer(Mean_Green_Norm ~ (1|Metadata_Stiffness:Metadata_Experiment:Metadata_Block:Replicate)+
                Metadata_Stiffness+ CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin + Abb_ECM + Metadata_Stiffness:(CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin)+ Metadata_Stiffness:Abb_ECM + Abb_ECM:(CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin), data = DMSOdsewithrep)

ecadmodel2 <- lmer(Mean_Red_Norm ~ (1|Metadata_Stiffness:Metadata_Experiment:Metadata_Block:Replicate)+
                Metadata_Stiffness+ CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin + Abb_ECM + Metadata_Stiffness:(CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin)+ Metadata_Stiffness:Abb_ECM + Abb_ECM:(CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin), data = DMSOdsewithrep)

anova(vimmodel, vimmodel2)
anova(ecadmodel, ecadmodel2)
anova(pxrmodel, pxrmodel2)
```
## Drug Response Model
2-27-25 -- DID NOT RERUN!!! 
```{r}
Drugdsewithrep <- subset(combinedds_Ratio, Metadata_Treatment == "10 uM")

Drugdsewithrep$CollagenI <- relevel(as.factor(Drugdsewithrep$CollagenI), ref = 5)
Drugdsewithrep$CollagenIV <- relevel(as.factor(Drugdsewithrep$CollagenIV), ref = 5)
Drugdsewithrep$Laminin <- relevel(as.factor(Drugdsewithrep$Laminin), ref = 5)
Drugdsewithrep$Hyaluronic_Acid <- relevel(as.factor(Drugdsewithrep$Hyaluronic_Acid), ref = 5)
Drugdsewithrep$TenascinC <- relevel(as.factor(Drugdsewithrep$TenascinC), ref = 5)
Drugdsewithrep$Osteopontin <- relevel(as.factor(Drugdsewithrep$Osteopontin), ref = 5)
Drugdsewithrep$Galectin3 <- relevel(as.factor(Drugdsewithrep$Galectin3), ref = 5)
Drugdsewithrep$Fibronectin <- relevel(as.factor(Drugdsewithrep$Fibronectin), ref = 5)
Drugdsewithrep$Decorin <- relevel(as.factor(Drugdsewithrep$Decorin), ref = 5)


vimmodeldrug <- lmer(Mean_Orange_Norm ~ (1|Metadata_Stiffness:Metadata_Experiment:Metadata_Block:Replicate)+
                Metadata_Stiffness+ CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin + Abb_ECM + Metadata_Stiffness:(CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin)+ Metadata_Stiffness:Abb_ECM + Abb_ECM:(CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin) + Metadata_Stiffness:Abb_ECM:(CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin), data = Drugdsewithrep)

ecadmodeldrug <- lmer(Mean_Red_Norm ~ (1|Metadata_Stiffness:Metadata_Experiment:Metadata_Block:Replicate)+
                Metadata_Stiffness+ CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin + Abb_ECM + Metadata_Stiffness:(CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin)+ Metadata_Stiffness:Abb_ECM + Abb_ECM:(CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin) + Metadata_Stiffness:Abb_ECM:(CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin), data = Drugdsewithrep)

pxrmodeldrug <- lmer(Mean_Green_Norm ~ (1|Metadata_Stiffness:Metadata_Experiment:Metadata_Block:Replicate)+
                Metadata_Stiffness+ CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin + Abb_ECM + Metadata_Stiffness:(CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin)+ Metadata_Stiffness:Abb_ECM + Abb_ECM:(CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin) + Metadata_Stiffness:Abb_ECM:(CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin), data = Drugdsewithrep)

dispersion_glmer(vimmodeldrug)
dispersion_glmer(ecadmodeldrug)
dispersion_glmer(pxrmodeldrug)
```
### Drug Anova
```{r}
vimanovadrug <- anova(vimmodeldrug)
ecadanovadrug <- anova(ecadmodeldrug)
pxranovadrug <- anova(pxrmodeldrug)
```

WP: 1 - pf(F-value, 1, 2)
SP: 1 -pf(F-value, df, 1168) (1168 = 1406 (total number of obs) - 1 - 233 (observed dfs))
```{r}
sum(vimanovadrug$npar)

vimanovadrug <- vimanovadrug %>% mutate(p_value = ifelse(row.names(vimanovadrug) == "Stiffness", 1 - pf(vimanovadrug$`F value`, 1, 2), 1 - pf(vimanovadrug$`F value`, vimanovadrug$npar, 1168)))

ecadanovadrug <- ecadanovadrug %>% mutate(p_value = ifelse(row.names(ecadanovadrug) == "Stiffness", 1 - pf(ecadanovadrug$`F value`, 1, 2), 1 - pf(ecadanovadrug$`F value`, ecadanovadrug$npar, 1168)))

pxranovadrug <- pxranovadrug %>% mutate(p_value = ifelse(row.names(pxranovadrug) == "Stiffness", 1 - pf(pxranovadrug$`F value`, 1, 2), 1 - pf(pxranovadrug$`F value`, pxranovadrug$npar, 1168)))

vimanovadrug <- vimanovadrug %>% mutate(psig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      p_value < 0.1   ~ ".",
      TRUE            ~ "ns"))

ecadanovadrug <- ecadanovadrug %>% mutate(psig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      p_value < 0.1   ~ ".",
      TRUE            ~ "ns"))

pxranovadrug <- pxranovadrug %>% mutate(psig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      p_value < 0.1   ~ ".",
      TRUE            ~ "ns"))
```

### Summary of Results
Key Takeaways: Stiffness is not a significant main factor  -> main factors still interpretable for Vim and PXR
Ecad has one 3-way interaction factor - Stiff:HA:ECM

Ratio: Vim is significantly impacted by ratio (all but C1,TC, FN), ECAD sig impacted by C1, C4, LN, and G3 Ratio, PXR by C1, LN, G3


Abb_ECM is sig for all channels

Stiffness and Ratio Intx: Not sig for any

Stiffness and ECM: Not sig for any

Abb_ECM & Ratio: Vim significant for C1, TC, LN, FN, and G3; while PXR only significant for TC and FN; ECAD sig for HA and TC

Different than DMSO Control :)

```{r}
vimpvaluedrug <- vimanovadrug[c("p_value", "psig")]
ecadpvaluedrug <- ecadanovadrug[c("p_value", "psig")]
pxrpvaluedrug <- pxranovadrug[c("p_value", "psig")]

colnames(vimpvaluedrug) <- c("Vim p_value", "Vim psig")
colnames(ecadpvaluedrug) <- c("Ecad p_value", "Ecad psig")
colnames(pxrpvaluedrug) <- c("PXR p_value", "PXR psig")

anovaoverviewdrug <- cbind(vimpvaluedrug, ecadpvaluedrug, pxrpvaluedrug)
```

### ICCs
```{r}
library(performance)
icc(vimmodeldrug)
icc(ecadmodeldrug)
icc(pxrmodeldrug)
```


### R2
```{r}
r2_nakagawa(vimmodeldrug)
r2_nakagawa(ecadmodeldrug)
r2_nakagawa(pxrmodeldrug)
```
## Testing Other Things
```{r}
library(lme4)
test1 <- lmer(Mean_Green_Norm ~ (1|Metadata_Stiffness:(Metadata_Experiment:Metadata_Block:Replicate))+
                Metadata_Stiffness + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin + Metadata_Stiffness:(CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin), data = DMSOdsewithrep)

test15  <- lmer(Mean_Green_Norm ~ (1|Metadata_Stiffness:Metadata_Experiment:Metadata_Block:Replicate)+
                Metadata_Stiffness+ Conditions +  Metadata_Stiffness:Conditions, data = DMSOdsewithrep)

test2 <- lmer(Mean_Green_Norm ~ (1|Metadata_Stiffness:Metadata_Experiment:Metadata_Block:Replicate)+
                Metadata_Stiffness + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin + Abb_ECM + Metadata_Stiffness:( CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin)+ Metadata_Stiffness:Abb_ECM , data = DMSOdsewithrep)


test3 <- lmer(Mean_Green_Norm ~ (1|Metadata_Stiffness:Metadata_Experiment:Metadata_Block:Replicate)+
                Metadata_Stiffness+  CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin + Abb_ECM + Metadata_Stiffness:( CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin)+ Metadata_Stiffness:Abb_ECM + Abb_ECM:( CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin) , data = DMSOdsewithrep)

test35 <- lmer(Mean_Green_Norm ~ (1|Metadata_Stiffness:Metadata_Experiment:Metadata_Block:Replicate)+
                Metadata_Stiffness+ Metadata_Stiffness*(Metadata_Ratio)+ Metadata_Stiffness:Abb_ECM + Abb_ECM*Metadata_Ratio , data = DMSOdsewithrep)

test4 <- lmer(Mean_Green_Norm ~ (1|Metadata_Stiffness:Metadata_Experiment:Metadata_Block:Replicate)+
                Metadata_Stiffness+  CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin + Abb_ECM + Metadata_Stiffness:( CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin)+ Metadata_Stiffness:Abb_ECM + Abb_ECM:( CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin) + Metadata_Stiffness:Abb_ECM:( CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin), data = DMSOdsewithrep)

anova(test1, test15, test2, test3, test35, test4)
```

```{r}

DMSOdsewithrep <- subset(combinedds_Ratio, Metadata_Treatment == "DMSO")
test3 <- lmer(Mean_Green_Norm ~ (1|Metadata_Stiffness:Metadata_Experiment:Metadata_Block:Replicate)+
                Metadata_Stiffness+  CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin + Abb_ECM + Metadata_Stiffness:(CollagenI +  CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin)+ Metadata_Stiffness:Abb_ECM + Abb_ECM:(CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin) , data = DMSOdsewithrep) 

test6 <- lmer(Mean_Green_Norm ~ (1|Metadata_Stiffness:Metadata_Experiment:Metadata_Block:Replicate)+  Metadata_Stiffness+  poly(CollagenI,2)  + poly(CollagenIV,2) + poly(Hyaluronic_Acid,2) + poly(TenascinC,2) + poly(Laminin,2)  + poly(Fibronectin,2) + poly(Galectin3,2) + poly(Osteopontin,2) + poly(Decorin,2) + Abb_ECM + Metadata_Stiffness:(CollagenI+ CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin)+ Metadata_Stiffness:Abb_ECM + Abb_ECM:( CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin) , data = DMSOdsewithrep) 

anova(test3, test6, pxrmodel)
```

```{r}
residuals3 <- resid(test3)
residuals6 <- resid(test6)

residualspxr <- resid(pxrmodel)

fitted3 <- fitted(test3)
fitted6 <- fitted(test6)
fittedpxr <- fitted(pxrmodel)

plot(fitted3, residuals3)

plot(fitted6, residuals6)

plot(fittedpxr, residualspxr)

qqnorm(residuals3, main = "Q-Q Plot of Residuals")
qqnorm(residuals6, main = "Q-Q Plot of Residuals")
qqnorm(residualspxr, main = "Q-Q Plot of Residuals")

hist(residuals3, breaks = 30)
hist(residuals6, breaks = 30)
hist(residualspxr, breaks = 30)
```

###Random effect structure 
Random effect structure is specified by Exp:Block:Rep which accounts for the random effects without overfitting the model to a Singular Fit
```{r}
test5<- lmer(Mean_Green_Norm ~ 
               #(1|Metadata_Experiment:Metadata_Block)+ 
               (1|Metadata_Experiment:Metadata_Block:Replicate) + 
                Metadata_Stiffness+  CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin + Abb_ECM + Metadata_Stiffness:( CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin)+ Metadata_Stiffness:Abb_ECM + Abb_ECM:( CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin) + Metadata_Stiffness:Abb_ECM:(CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin), data = DMSOdsewithrep)

anova(test4, test5)
```

##Mixture Design Exploration
```{r}
library(mixexp)
mix_design <- SLD(9,4)

DMSOdsewithrep %>% group_by(CollagenI, CollagenIV) %>% summarize(Mean_Green_Norm = mean(Mean_Green_Norm)) %>% ggplot(DMSOdsewithrep, aes(x = CollagenI, y = CollagenIV)) +
geom_point(aes(color =Mean_Green_Norm, size = Mean_Green_Norm), na.rm = TRUE) +
labs(x = "Collagen I", y = "Collagen IV") +
theme_minimal()

```

```{r}
library(lme4)
test10 <- lmer(Mean_Green_Norm ~ (1|Metadata_Stiffness:Metadata_Experiment:Metadata_Block:Replicate)+
                Metadata_Stiffness +  poly(CollagenI,2)  + poly(CollagenIV,2) + poly(Hyaluronic_Acid,2) + poly(TenascinC,2) + poly(Laminin,2)  + poly(Fibronectin,2) + poly(Galectin3,2) + poly(Osteopontin,2) + poly(Decorin,2) +  CollagenI * CollagenIV + 
               CollagenI * Hyaluronic_Acid + 
               CollagenI * TenascinC + 
               CollagenI * Laminin + 
               CollagenI * Fibronectin + 
               CollagenI * Galectin3 + 
               CollagenI * Osteopontin + 
               CollagenI * Decorin +
               
               CollagenIV * Hyaluronic_Acid + 
               CollagenIV * TenascinC + 
               CollagenIV * Laminin + 
               CollagenIV * Fibronectin + 
               CollagenIV * Galectin3 + 
               CollagenIV * Osteopontin + 
               CollagenIV * Decorin +
               
               Hyaluronic_Acid * TenascinC + 
               Hyaluronic_Acid * Laminin + 
               Hyaluronic_Acid * Fibronectin + 
               Hyaluronic_Acid * Galectin3 + 
               Hyaluronic_Acid * Osteopontin + 
               Hyaluronic_Acid * Decorin +
               
               TenascinC * Laminin + 
               TenascinC * Fibronectin + 
               TenascinC * Galectin3 + 
               TenascinC * Osteopontin + 
               TenascinC * Decorin +
               
               Laminin * Fibronectin + 
               Laminin * Galectin3 + 
               Laminin * Osteopontin + 
               Laminin * Decorin +
               
               Fibronectin * Galectin3 + 
               Fibronectin * Osteopontin + 
               Fibronectin * Decorin +
               
               Galectin3 * Osteopontin + 
               Galectin3 * Decorin +
               
               Osteopontin * Decorin + Metadata_Stiffness:(CollagenI +  CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin) , data = DMSOdsewithrep) 

anova(test3, pxrmodel, test10)
```

```{r}
residuals10 <- resid(test10)

fitted10 <- fitted(test10)

plot(fitted10, residuals10)


qqnorm(residuals10, main = "Q-Q Plot of Residuals")

hist(residuals10, breaks = 30)

```
NOT CLR -> Literally the same as making them factors... so no point - another rabbit hole.
```{r}
library(lme4)
ecm_data <- DMSOdsewithrep[, c("CollagenI", "CollagenIV", "Hyaluronic_Acid", "Laminin" ,        "TenascinC" ,      "Galectin3"    ,   "Fibronectin" ,    "Osteopontin"   ,  "Decorin")]
ecm_data_clr<- clr(ecm_data + 0.0000001)

colnames(ecm_data_clr) <- c("CollagenI_CLR", "CollagenIV_CLR", "Hyaluronic_Acid_CLR", "Laminin_CLR" ,        "TenascinC_CLR" ,      "Galectin3_CLR"    ,   "Fibronectin_CLR" ,    "Osteopontin_CLR"   ,  "Decorin_CLR")
DMSOdsewithrep <- cbind(DMSOdsewithrep, ecm_data_clr)

# testnclr <- lmer(Mean_Green_Norm ~ (1|Metadata_Stiffness:Metadata_Experiment:Metadata_Block:Replicate)+
#                 Metadata_Stiffness+  CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin + Abb_ECM + Metadata_Stiffness:( CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin)+ Metadata_Stiffness:Abb_ECM + Abb_ECM:( CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin) , data = testDMSOwithclr)
# 
# test6nclr <- lmer(Mean_Green_Norm ~ (1|Metadata_Stiffness:Metadata_Experiment:Metadata_Block:Replicate)+  Metadata_Stiffness+  poly(CollagenI,2)  + poly(CollagenIV,2) + poly(Hyaluronic_Acid,2) + poly(TenascinC,2) + poly(Laminin,2)  + poly(Fibronectin,2) + poly(Galectin3,2) + poly(Osteopontin,2) + poly(Decorin,2) + Abb_ECM + Metadata_Stiffness:(CollagenI+ CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin)+ Metadata_Stiffness:Abb_ECM + Abb_ECM:( CollagenI + CollagenIV + Hyaluronic_Acid + TenascinC + Laminin + Fibronectin + Galectin3 + Osteopontin + Decorin) , data = testDMSOwithclr) 

testclr <- lmer(Mean_Green_Norm ~ (1|Metadata_Stiffness:Metadata_Experiment:Metadata_Block:Replicate)+
                Metadata_Stiffness+  CollagenI_CLR + CollagenIV_CLR + Hyaluronic_Acid_CLR + TenascinC_CLR + Laminin_CLR + Fibronectin_CLR + Galectin3_CLR + Osteopontin_CLR + Decorin_CLR + Abb_ECM + Metadata_Stiffness:(CollagenI_CLR +  CollagenIV_CLR + Hyaluronic_Acid_CLR + TenascinC_CLR + Laminin_CLR + Fibronectin_CLR + Galectin3_CLR + Osteopontin_CLR + Decorin_CLR)+ Metadata_Stiffness:Abb_ECM + Abb_ECM:(CollagenI_CLR + CollagenIV_CLR + Hyaluronic_Acid_CLR + TenascinC_CLR + Laminin_CLR + Fibronectin_CLR + Galectin3_CLR + Osteopontin_CLR + Decorin_CLR) + Metadata_Stiffness:Abb_ECM:(CollagenI_CLR +  CollagenIV_CLR + Hyaluronic_Acid_CLR + TenascinC_CLR + Laminin_CLR + Fibronectin_CLR + Galectin3_CLR + Osteopontin_CLR + Decorin_CLR) , data = DMSOdsewithrep) 

anova(testclr,pxrmodel)
```

