---
title: "Setting up the Data"
output: html_document
date: "2025-02-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Library Loading
```{r}
library(dplyr)
library(tidyr)
library(ggpubr)
library(ggplot2)
library(ggprism)
```

Load in blue_objects, red_objects, green_objects, and orange_objects prior to running
```{r}
library(readr)
blue_objects <- read_csv("data/blue_objects.csv", 
 col_types = cols(Metadata_Column...5 = col_skip(), 
 Metadata_Row...10 = col_skip(), Metadata_Scene...12 = col_skip(), 
Metadata_Slide...15 = col_skip()))

red_objects <- read_csv("data/red_objects.csv", 
 col_types = cols(Metadata_Column...5 = col_skip(), 
 Metadata_Row...10 = col_skip(), Metadata_Scene...12 = col_skip(), 
Metadata_Slide...15 = col_skip()))

green_objects <- read_csv("data/green_objects.csv", 
 col_types = cols(Metadata_Column...5 = col_skip(), 
 Metadata_Row...10 = col_skip(), Metadata_Scene...12 = col_skip(), 
Metadata_Slide...15 = col_skip()))

orange_objects <- read_csv("data/orange_objects.csv", 
 col_types = cols(Metadata_Column...5 = col_skip(), 
 Metadata_Row...10 = col_skip(), Metadata_Scene...12 = col_skip(), 
Metadata_Slide...15 = col_skip()))
```

## Creating Dataset
```{r Choosing Subsets}
greencols <- c("AreaShape_Area","Intensity_IntegratedIntensity_green","Intensity_MeanIntensityEdge_green","Intensity_MeanIntensity_green")

redcols <- c("AreaShape_Area","Intensity_IntegratedIntensity_Red","Intensity_MeanIntensityEdge_Red","Intensity_MeanIntensity_Red")

orangecols <- c("ImageNumber", "ObjectNumber", "AreaShape_Area","Intensity_IntegratedIntensity_Orange","Intensity_MeanIntensityEdge_Orange","Intensity_MeanIntensity_Orange")

green <- subset(green_objects, select = greencols)

red <- subset(red_objects, select = redcols)

orange <- subset(orange_objects, select = orangecols)

colnames(green) <- c("AreaShape_Area_Green", "Intensity_IntegratedIntensity_Green", "Intensity_MeanIntensityEdge_Green","Intensity_MeanIntensity_Green")

colnames(red) <- c("AreaShape_Area_Red", "Intensity_IntegratedIntensity_Red", "Intensity_MeanIntensityEdge_Red","Intensity_MeanIntensity_Red")

colnames(orange) <- c("ImageNumber", "ObjectNumber","AreaShape_Area_Orange", "Intensity_IntegratedIntensity_Orange", "Intensity_MeanIntensityEdge_Orange","Intensity_MeanIntensity_Orange")
```

99.61% cells remain 974284/978035 (99.61%)
```{r Merge All Together}
all_objects <- cbind(blue_objects, green, red)

all_objects <- left_join(all_objects, orange, by = c("ImageNumber", "ObjectNumber"))

all_objects <- subset(all_objects, AreaShape_Area_Green <= 1000)
all_objects <- subset(all_objects, AreaShape_Area_Red <= 1000)
# all_objects <- subset(all_objects, AreaShape_Area_Orange <= 1000)
```

### Assigning Conditions
```{r Assigning Conditions}
all_objects <- all_objects %>% mutate(
Metadata_Stiffness = ifelse(Metadata_Slide...14%in% c("01", "04", "05", "07", "11", "12", "15", "16", "18", "21", "22", "23"), "1kPa", "25kPa"), 
Metadata_Treatment = ifelse(Metadata_Slide...14 %in% c("01", "02", "03", "04", "05", "06","13", "14", "15", "22", "23", "24"), "DMSO", "10 uM"))

unique(all_objects$Metadata_Stiffness)
unique(all_objects$Metadata_Treatment)
```

```{r Renaming Columns To Get Rid of Ellipses}
all_objects <- all_objects %>%
  rename("Metadata_Column"="Metadata_Column...4",
         "Metadata_Scene" = "Metadata_Scene...11",
         "Metadata_Slide" = "Metadata_Slide...14",
         "Metadata_Row" = "Metadata_Row...9")

```

```{r Splitting Experiments}
e1_objects <- all_objects[all_objects$Metadata_Slide %in% c("01", "02" ,"03", "04", "05", "06", "07", "08", "09", "10", "11", "12"),]
e1_objects$Metadata_Experiment <- "E1"
e2_objects <- all_objects[all_objects$Metadata_Slide %in% c("13", "14" ,"15", "16", "17", "18", "19", "20", "21", "22", "23", "24"),]
e2_objects$Metadata_Experiment <- "E2"
```

Load in DREMT Conditions e1 and e2
```{r Assigning ECMs}
columns <- c("Metadata_Column", "Metadata_Row", "Metadata_ECMs", "Metadata_Ratio")

colnames(DREMT_Conditions_e1) <- columns
colnames(DREMT_Conditions_e2) <- columns

ECMs$Metadata_Ratio[ECMs$Metadata_Ratio == "\"50:50\""] <- "50/50"
ECMs$Metadata_Ratio[ECMs$Metadata_Ratio == "\"75:25\"" ] <- "75/25"
ECMs$Metadata_Ratio[ECMs$Metadata_Ratio == "25:75" ] <- "25/75"

DREMT_Conditions_e1 <- merge(DREMT_Conditions_e1, ECMs)
DREMT_Conditions_e2 <- merge(DREMT_Conditions_e2, ECMs)
```

```{r Assigning ECMs to Experiments}
e1_objectsECM <- join(e1_objects,DREMT_Conditions_e1)
e2_objectsECM <- join(e2_objects,DREMT_Conditions_e2)
```

```{r RBIND to final objects}
objects_full <- rbind(e1_objectsECM,e2_objectsECM)
objects_full <- subset(objects_full, Metadata_ECMs != "Dextran")
```

## Quantile Distribution
There is some variability in the distributions of the fluorescent markers... so we are using a technique suggested by Kerim in his JoVE paper in 2017, quantile normalization for biological replicates

```{r}
objects_full_FORNORM <- subset(objects_full, select = c("ImageNumber", "ObjectNumber", "Metadata_Column","Metadata_Experiment",
                                                     "Metadata_Row", "Metadata_Scene", "Metadata_Slide", "Metadata_Stiffness", 
                                                     "Metadata_Treatment", "Metadata_ECMs", "Metadata_Ratio", "Abb_ECM",
                                                     "Intensity_MeanIntensity_Orange", "Intensity_MeanIntensity_Green", 
                                                     "Intensity_MeanIntensity_Red") )

E1_1217_ForNorm <- subset(objects_full_FORNORM, Metadata_Experiment == "E1")

E2_1217_ForNorm <- subset(objects_full_FORNORM, Metadata_Experiment == "E2")

```

## ECAD Quantile Normalization

1. Created a common set of percentile ranks (0 to 100) to align both columns
2. Interpolated the values of both columns to match the common_ranks 
3. Perform Quantile Normalization on these common ranks interpolated values
4. Used original ranks of each experiment to assign new quantile values

```{r}
sorted_ecad1 <- sort(E1_1217_ForNorm$Intensity_MeanIntensity_Red) 
sorted_ecad2 <- sort(E2_1217_ForNorm$Intensity_MeanIntensity_Red)

common_ranks <- seq(0, 1, length.out = max(length(sorted_ecad1), length(sorted_ecad2)))

interp_ecad1 <- approx(seq(0, 1, length.out = length(sorted_ecad1)), sorted_ecad1, xout = common_ranks)$y
interp_ecad2 <- approx(seq(0, 1, length.out = length(sorted_ecad2)), sorted_ecad2, xout = common_ranks)$y

avg_quantiles_ecad <- rowMeans(cbind(interp_ecad1, interp_ecad2))

ranksecad1 <- rank(E1_1217_ForNorm$Intensity_MeanIntensity_Red, ties.method = "average") / length(E1_1217_ForNorm$Intensity_MeanIntensity_Red)

ranksecad2 <- rank(E2_1217_ForNorm$Intensity_MeanIntensity_Red, ties.method = "average") / length(E2_1217_ForNorm$Intensity_MeanIntensity_Red)

# Map the averaged quantiles back to the original ranks
normalized_ecad1 <- approx(common_ranks, avg_quantiles_ecad, xout = ranksecad1, rule = 2)$y
normalized_ecad2 <- approx(common_ranks, avg_quantiles_ecad, xout = ranksecad2, rule = 2)$y

# Check results
head(normalized_ecad1)
head(normalized_ecad2)

summary(normalized_ecad1)
summary(normalized_ecad2)

hist(normalized_ecad1)
hist(normalized_ecad2)
```

## Vim Quantile Normalization
```{r}
sorted_vim1 <- sort(E1_1217_ForNorm$Intensity_MeanIntensity_Orange) 
sorted_vim2 <- sort(E2_1217_ForNorm$Intensity_MeanIntensity_Orange)

common_ranks <- seq(0, 1, length.out = max(length(sorted_vim1), length(sorted_vim2)))

interp_vim1 <- approx(seq(0, 1, length.out = length(sorted_vim1)), sorted_vim1, xout = common_ranks)$y
interp_vim2 <- approx(seq(0, 1, length.out = length(sorted_vim2)), sorted_vim2, xout = common_ranks)$y

avg_quantiles_vim <- rowMeans(cbind(interp_vim1, interp_vim2))

ranksvim1 <- rank(E1_1217_ForNorm$Intensity_MeanIntensity_Orange, ties.method = "average") / length(E1_1217_ForNorm$Intensity_MeanIntensity_Orange)
ranksvim2 <- rank(E2_1217_ForNorm$Intensity_MeanIntensity_Orange, ties.method = "average") / length(E2_1217_ForNorm$Intensity_MeanIntensity_Orange)

# Map the averaged quantiles back to the original ranks
normalized_vim1 <- approx(common_ranks, avg_quantiles_vim, xout = ranksvim1, rule = 2)$y
normalized_vim2 <- approx(common_ranks, avg_quantiles_vim, xout = ranksvim2, rule = 2)$y

# Check results
head(normalized_vim1)
head(normalized_vim2)

summary(normalized_vim1)
summary(normalized_vim2)

hist(normalized_vim1)
hist(normalized_vim2)
```

## PXR Quantile Normalization
```{r}
sorted_pxr1 <- sort(E1_1217_ForNorm$Intensity_MeanIntensity_Green) 
sorted_pxr2 <- sort(E2_1217_ForNorm$Intensity_MeanIntensity_Green)

common_ranks <- seq(0, 1, length.out = max(length(sorted_pxr1), length(sorted_pxr2)))

interp_pxr1 <- approx(seq(0, 1, length.out = length(sorted_pxr1)), sorted_pxr1, xout = common_ranks)$y
interp_pxr2 <- approx(seq(0, 1, length.out = length(sorted_pxr2)), sorted_pxr2, xout = common_ranks)$y

avg_quantiles_pxr <- rowMeans(cbind(interp_pxr1, interp_pxr2))

rankspxr1 <- rank(E1_1217_ForNorm$Intensity_MeanIntensity_Green, ties.method = "average") / length(E1_1217_ForNorm$Intensity_MeanIntensity_Green)
rankspxr2 <- rank(E2_1217_ForNorm$Intensity_MeanIntensity_Green, ties.method = "average") / length(E2_1217_ForNorm$Intensity_MeanIntensity_Green)

# Map the averaged quantiles back to the original ranks
normalized_pxr1 <- approx(common_ranks, avg_quantiles_pxr, xout = rankspxr1, rule = 2)$y
normalized_pxr2 <- approx(common_ranks, avg_quantiles_pxr, xout = rankspxr2, rule = 2)$y

# Check results
head(normalized_pxr1)
head(normalized_pxr2)

summary(normalized_pxr1)
summary(normalized_pxr2)

hist(normalized_pxr1)
hist(normalized_pxr2)
```

## Adding the New Normalized Values to objects_full for further analysis
### E1
```{r}
E1_1217_ForNorm <- cbind(E1_1217_ForNorm, normalized_ecad1)
E1_1217_ForNorm <- cbind(E1_1217_ForNorm, normalized_vim1)
E1_1217_ForNorm <- cbind(E1_1217_ForNorm, normalized_pxr1)

colnames(E1_1217_ForNorm)[which(names(E1_1217_ForNorm) == "normalized_ecad1")] <- "Normalized_Ecad"
colnames(E1_1217_ForNorm)[which(names(E1_1217_ForNorm) == "normalized_vim1")] <- "Normalized_Vimentin"
colnames(E1_1217_ForNorm)[which(names(E1_1217_ForNorm) == "normalized_pxr1")] <- "Normalized_PXR"
```

### E2
```{r}
E2_1217_ForNorm <- cbind(E2_1217_ForNorm, normalized_ecad2)
E2_1217_ForNorm <- cbind(E2_1217_ForNorm, normalized_vim2)
E2_1217_ForNorm <- cbind(E2_1217_ForNorm, normalized_pxr2)

colnames(E2_1217_ForNorm)[which(names(E2_1217_ForNorm) == "normalized_ecad2")] <- "Normalized_Ecad"
colnames(E2_1217_ForNorm)[which(names(E2_1217_ForNorm) == "normalized_vim2")] <- "Normalized_Vimentin"
colnames(E2_1217_ForNorm)[which(names(E2_1217_ForNorm) == "normalized_pxr2")] <- "Normalized_PXR"

```

### Putting it all Back Together
```{r}
objects_full_Norm <- rbind(E1_1217_ForNorm, E2_1217_ForNorm)
```
## Summarizing objects
### Summarizing to island (ds_s_pheno)
```{r}
ds_s_pheno <- ddply(objects_full_Norm, 
               .(Metadata_Slide, 
                 Metadata_Stiffness,
                 Metadata_Scene,
                 Metadata_Experiment, 
                 Metadata_Row,
                 Metadata_Treatment,
                 Metadata_Column,
                 Metadata_Ratio,
                 Metadata_ECMs,
                 Abb_ECM), 
               summarize,
               
               ## Nuclei Count
               Nuclei = length(ObjectNumber),
               logNuclei = log(length(ObjectNumber)),
               
               ## Green PXR Channel Analysis
               Mean_Green = mean(Intensity_MeanIntensity_Green),
               SD_Green = sd(Intensity_MeanIntensity_Green),
               Mean_Green_Norm = mean(Normalized_PXR),
               SD_Green_Norm = sd(Normalized_PXR),
               
               ## Red Ecad Channel Analysis
               Mean_Red = mean(Intensity_MeanIntensity_Red),
               SD_Red = sd(Intensity_MeanIntensity_Red),
               Mean_Red_Norm = mean(Normalized_Ecad),
               SD_Red_Norm = sd(Normalized_Ecad),
               
               ## Orange Vimentin Channel Analysis
               Mean_Orange = mean(Intensity_MeanIntensity_Orange),
               SD_Orange = sd(Intensity_MeanIntensity_Orange),
               Mean_Orange_Norm = mean(Normalized_Vimentin),
               SD_Orange_Norm = sd(Normalized_Vimentin)
)
```


### Summarizing to Slide (ds_e_pheno)
```{r}
ds_e_pheno <- ddply(ds_s_pheno, 
               .(Metadata_Slide, 
                 Metadata_Stiffness,
                 Metadata_Experiment, 
                 Metadata_Row,
                 Metadata_Treatment,
                 Metadata_Column,
                 Metadata_Ratio,
                 Metadata_ECMs,
                 Abb_ECM), 
               summarize,
               
               ## Nuclei Count
               Mean_Nuclei = mean(Nuclei),
               SD_Nuclei = sd(Nuclei),
               Mean_logNuclei = mean(logNuclei),
               SD_logNuclei = sd(logNuclei),
               
               ## Green PXR Channel Analysis
               Mean_Green = mean(Mean_Green),
               SD_Green = sqrt(sum(SD_Green^2)/NROW(SD_Green)),
               Mean_Green_Norm = mean(Mean_Green_Norm),
               SD_Green_Norm = sqrt(sum(SD_Green_Norm^2)/NROW(SD_Green_Norm)),
               
               ## Red Ecad Channel Analysis
               Mean_Red = mean(Mean_Red),
               SD_Red = sqrt(sum(SD_Red^2)/NROW(SD_Red)),
               Mean_Red_Norm = mean(Mean_Red_Norm),
               SD_Red_Norm = sqrt(sum(SD_Red_Norm^2)/NROW(SD_Red_Norm)),
               
               ## Orange Vimentin Channel Analysis
               Mean_Orange = mean(Mean_Orange),
               SD_Orange = sqrt(sum(SD_Orange^2)/NROW(SD_Orange)),
               Mean_Orange_Norm = mean(Mean_Orange_Norm),
               SD_Orange_Norm = sqrt(sum(SD_Orange_Norm^2)/NROW(SD_Orange_Norm))
)
```

### Summarizing to Experiment (ds_pheno)
```{r}
ds_pheno <- ddply(ds_e_pheno, 
               .(Metadata_Stiffness,
                 Metadata_Experiment, 
                 Metadata_Row,
                 Metadata_Treatment,
                 Metadata_Column,
                 Metadata_Ratio,
                 Metadata_ECMs,
                 Abb_ECM), 
               summarize,
               
               ## Nuclei Count
               Mean_Nuclei = mean(Mean_Nuclei),
               SD_Nuclei = sqrt(sum(SD_Nuclei^2)/NROW(SD_Nuclei)),
               Mean_logNuclei = mean(Mean_logNuclei),
               SD_logNuclei = sqrt(sum(SD_logNuclei^2)/NROW(SD_logNuclei)),
               
               ## Green PXR Channel Analysis
               Mean_Green = mean(Mean_Green),
               SD_Green = sqrt(sum(SD_Green^2)/NROW(SD_Green)),
               Mean_Green_Norm = mean(Mean_Green_Norm),
               SD_Green_Norm = sqrt(sum(SD_Green_Norm^2)/NROW(SD_Green_Norm)),
               
               ## Red Ecad Channel Analysis
               Mean_Red = mean(Mean_Red),
               SD_Red = sqrt(sum(SD_Red^2)/NROW(SD_Red)),
               Mean_Red_Norm = mean(Mean_Red_Norm),
               SD_Red_Norm = sqrt(sum(SD_Red_Norm^2)/NROW(SD_Red_Norm)),
               
               ## Orange Vimentin Channel Analysis
               Mean_Orange = mean(Mean_Orange),
               SD_Orange = sqrt(sum(SD_Orange^2)/NROW(SD_Orange)),
               Mean_Orange_Norm = mean(Mean_Orange_Norm),
               SD_Orange_Norm = sqrt(sum(SD_Orange_Norm^2)/NROW(SD_Orange_Norm))
)
```

## Writing CSVs
```{r}
write.csv(ds_s_pheno, "ds_s_pheno.csv")
write.csv(ds_e_pheno, "ds_e_pheno.csv")
write.csv(ds_pheno, "ds_pheno.csv")
```

## Adding Blocks
A slide is off... check assignments... too many 10 uM 25 kPas
```{r}
ds_e_pheno %>% group_by(Metadata_Slide, Metadata_Treatment, Metadata_Stiffness) %>% summarize(count=n())

ds_e_pheno  <- ds_e_pheno%>%mutate(Metadata_Block = ifelse(Metadata_Stiffness == "1kPa", ifelse(Metadata_Treatment == "DMSO", "1", "2"), ifelse(Metadata_Treatment == "10 uM", "3", "4")))

unique(ds_e_pheno$Metadata_Block)

ds_e_pheno %>% group_by( Metadata_Block) %>% summarize(count=n())
```

```{r}
combined_dsRatio <- subset(ds_e_pheno, Metadata_Ratio %in% c("100", "50/50", "75/25", "25/75"))
combined_dsRatio <- subset(ds_e_pheno, Metadata_ECMs != "Dextran")

combined_dsRatio$CollagenI <- NA
combined_dsRatio$CollagenIV <- NA
combined_dsRatio$Laminin <- NA
combined_dsRatio$Hyaluronic_Acid <- NA
combined_dsRatio$TenascinC<- NA
combined_dsRatio$Osteopontin <- NA
combined_dsRatio$Galectin3 <- NA
combined_dsRatio$Fibronectin <- NA
combined_dsRatio$Decorin <- NA


C1100 <- list(1,0,0,0,0,0,0,0,0)
C1C425 <- list(0.25,0.75,0,0,0,0,0,0,0)
C1C450 <- list(0.5,0.5,0,0,0,0,0,0,0)
C1C475 <- list(0.75,0.25,0,0,0,0,0,0,0)
C1LN25 <- list(0.25,0,0.75,0,0,0,0,0,0)
C1LN50 <- list(0.5,0,0.5,0,0,0,0,0,0)
C1LN75 <- list(0.75,0,0.25,0,0,0,0,0,0)
C1HA25 <- list(0.25,0,0,0,0.75,0,0,0,0)
C1HA50 <- list(0.5,0,0,0,0,0.5,0,0,0)
C1HA75 <- list(0.75,0,0,0,0,0.25,0,0,0)
C1TC25 <- list(0.25,0,0,0.75,0,0,0,0,0)
C1TC50 <- list(0.5,0,0,0.5,0,0,0,0,0)
C1TC75 <- list(0.75,0,0,0.25,0,0,0,0,0)
C1OPN25 <- list(0.25,0,0,0,0,0.75,0,0,0)
C1OPN50 <- list(0.5,0,0,0,0,0.5,0,0,0)
C1OPN75  <- list(0.75,0,0,0,0,0.25,0,0,0)
C1DN25 <- list(0.25,0,0,0,0,0,0.75,0,0)
C1DN50 <- list(0.5,0,0,0,0,0,0.5,0,0)
C1DN75 <- list(0.75,0,0,0,0,0,0.25,0,0)
C1G325 <- list(0.25,0,0,0,0,0,0,0.75,0)
C1G350 <- list(0.5,0,0,0,0,0,0,0.5,0)
C1G375 <- list(0.75,0,0,0,0,0,0,0.25,0)
C1FN25 <- list(0.25,0,0,0,0,0,0,0,0.75)
C1FN50 <- list(0.5,0,0,0,0,0,0,0,0.5)
C1FN75 <- list(0.75,0,0,0,0,0,0,0,0.25)
C4100 <- list(0,1,0,0,0,0,0,0,0)
C4LN25 <- list(0,0.25,0.75,0,0,0,0,0,0)
C4LN50 <- list(0,0.5,0.5,0,0,0,0,0,0)
C4LN75 <- list(0,0.75,0.25,0,0,0,0,0,0)
C4TC25 <- list(0,0.25,0,0.75,0,0,0,0,0)
C4TC50 <- list(0,0.5,0,0.5,0,0,0,0,0)
C4TC75 <- list(0,0.75,0,0.25,0,0,0,0,0)
C4HA25 <- list(0,0.25,0,0,0.75,0,0,0,0)
C4HA50 <- list(0,0.5,0,0,0.5,0,0,0,0)
C4HA75 <- list(0,0.75,0,0,0.25,0,0,0,0)
C4OPN25 <- list(0,0.25,0,0,0,0.75,0,0,0)
C4OPN50 <- list(0,0.5,0,0,0,0.5,0,0,0)
C4OPN75 <- list(0,0.75,0,0,0,0.25,0,0,0)
C4DN25 <- list(0,0.25,0,0,0,0,0.75,0,0)
C4DN50 <- list(0,0.5,0,0,0,0,0.5,0,0)
C4DN75 <- list(0,0.75,0,0,0,0,0.25,0,0)
C4G325 <- list(0,0.25,0,0,0,0,0,0.75,0)
C4G350 <- list(0,0.5,0,0,0,0,0,0.5,0)
C4G375 <- list(0,0.75,0,0,0,0,0,0.25,0)
C4FN25 <- list(0,0.25,0,0,0,0,0,0.75,0)
C4FN50 <- list(0,0.5,0,0,0,0,0,0.5,0)
C4FN75 <- list(0,0.75,0,0,0,0,0,0.25,0)
LN100 <- list(0,0,1,0,0,0,0,0,0)
LNTC25 <- list(0,0,0.25,0.75,0,0,0,0,0)
LNTC50 <- list(0,0,0.5,0.5,0,0,0,0,0)
LNTC75 <- list(0,0,0.75,0.25,0,0,0,0,0)
LNHA25 <- list(0,0,0.25,0,0.75,0,0,0,0)
LNHA50 <- list(0,0,0.5,0,0.5,0,0,0,0)
LNHA75 <- list(0,0,0.75,0,0.25,0,0,0,0)
LNOPN25 <- list(0,0,0.25,0,0,0.75,0,0,0)
LNOPN50 <- list(0,0,0.5,0,0,0.5,0,0,0)
LNOPN75 <- list(0,0,0.75,0,0,0.25,0,0,0)
LNDN25 <- list(0,0,0.25,0,0,0,0.75,0,0)
LNDN50 <- list(0,0,0.5,0,0,0,0.5,0,0)
LNDN75 <- list(0,0,0.75,0,0,0,0.25,0,0)
LNG325 <- list(0,0,0.25,0,0,0,0,0.75,0)
LNG350 <- list(0,0,0.5,0,0,0,0,0.5,0)
LNG375 <- list(0,0,0.75,0,0,0,0,0.25,0)
LNFN25 <- list(0,0,0.25,0,0,0,0,0,0.75)
LNFN50 <- list(0,0,0.5,0,0,0,0,0,0.5)
LNFN75 <- list(0,0,0.75,0,0,0,0,0,0.25)
TC100 <- list(0,0,0,1,0,0,0,0,0)
TCHA25 <- list(0,0,0,0.25,0.75,0,0,0,0)
TCHA50 <- list(0,0,0,0.5,0.5,0,0,0,0)
TCHA75 <- list(0,0,0,0.75,0.25,0,0,0,0)
TCOPN25 <- list(0,0,0,0.25,0,0.75,0,0,0)
TCOPN50 <- list(0,0,0,0.5,0,0.5,0,0,0)
TCOPN75 <- list(0,0,0,0.75,0,0.25,0,0,0)
TCDN25 <- list(0,0,0,0.25,0,0,0.75,0,0)
TCDN50 <- list(0,0,0,0.5,0,0,0.5,0,0)
TCDN75 <- list(0,0,0,0.75,0,0,0.25,0,0)
TCG325 <- list(0,0,0,0.25,0,0,0,0.75,0)
TCG350 <- list(0,0,0,0.5,0,0,0,0.5,0)
TCG375 <- list(0,0,0,0.75,0,0,0,0.25,0)
TCFN25 <- list(0,0,0,0.25,0,0,0,0,0.75)
TCFN50 <- list(0,0,0,0.5,0,0,0,0,0.5)
TCFN75 <- list(0,0,0,0.75,0,0,0,0,0.25)
HA100 <- list(0,0,0,0,1,0,0,0,0)
HAOPN25 <- list(0,0,0,0,0.25,0.75,0,0,0)
HAOPN50 <- list(0,0,0,0,0.5,0.5,0,0,0)
HAOPN75 <- list(0,0,0,0,0.75,0.25,0,0,0)
HADN25 <- list(0,0,0,0,0.25,0,0.75,0,0)
HADN50 <- list(0,0,0,0,0.5,0,0.5,0,0)
HADN75 <- list(0,0,0,0,0.75,0,0.25,0,0)
HAG325 <- list(0,0,0,0,0.25,0,0,0.75,0)
HAG350 <- list(0,0,0,0,0.5,0,0,0.5,0)
HAG375 <- list(0,0,0,0,0.75,0,0,0.25,0)
HAFN25 <- list(0,0,0,0,0.25,0,0,0,0.75)
HAFN50 <- list(0,0,0,0,0.5,0,0,0,0.5)
HAFN75 <- list(0,0,0,0,0.75,0,0,0,0.25)
OPN100 <- list(0,0,0,0,0,1,0,0,0)
OPNDN25 <- list(0,0,0,0,0,0.25,0.75,0,0)
OPNDN50 <- list(0,0,0,0,0,0.5,0.5,0,0)
OPNDN75 <- list(0,0,0,0,0,0.75,0.25,0,0)
OPNG325 <- list(0,0,0,0,0,0.25,0,0.75,0)
OPNG350 <- list(0,0,0,0,0,0.5,0,0.5,0)
OPNG375 <- list(0,0,0,0,0,0.75,0,0.25,0)
OPNFN25 <- list(0,0,0,0,0,0.25,0,0,0.75)
OPNFN50 <- list(0,0,0,0,0,0.5,0,0,0.5)
OPNFN75 <- list(0,0,0,0,0,0.75,0,0,0.25)
DN100 <- list(0,0,0,0,0,0,1,0,0)
DNG325 <- list(0,0,0,0,0,0,0.25,0.75,0)
DNG350 <- list(0,0,0,0,0,0,0.5,0.5,0)
DNG375 <- list(0,0,0,0,0,0,0.75,0.25,0)
DNFN25 <- list(0,0,0,0,0,0,0.25,0,0.75)
DNFN50 <- list(0,0,0,0,0,0,0.5,0,0.5)
DNFN75 <- list(0,0,0,0,0,0,0.75,0,0.25)
G3100 <- list(0,0,0,0,0,0,0,1,0)
G3FN25 <- list(0,0,0,0,0,0,0,0.25,0.75)
G3FN50 <- list(0,0,0,0,0,0,0,0.5,0.5)
G3FN75 <- list(0,0,0,0,0,0,0,0.75,0.25)
FN100 <- list(0,0,0,0,0,0,0,0,1)

experimental_conditions <- list(
  "Collagen I" = list(
    "100" = C1100
  ),
  "Collagen ICollagen IV" = list(
    "25/75" = C1C425,
    "50/50" = C1C450,
    "75/25" = C1C475
  ),
  "Collagen ILaminin" = list(
    "25/75" = C1LN25,
    "50/50" = C1LN50,
    "75/25" = C1LN75
  ),
  "Collagen ITenascin C" = list(
    "25/75" = C1TC25,
    "50/50" = C1TC50,
    "75/25" = C1TC75
  ),
  "Collagen IHyaluronic Acid" = list(
    "25/75" = C1HA25,
    "50/50" = C1HA50,
    "75/25" = C1HA75
  ),
  "Collagen IOsteopontin" = list(
    "25/75" = C1OPN25,
    "50/50" = C1OPN50,
    "75/25" = C1OPN75
  ),
  "Collagen IDecorin" = list(
    "25/75" = C1DN25,
    "50/50" = C1DN50,
    "75/25" = C1DN75
  ),
  "Collagen IGalectin 3" = list(
    "25/75" = C1G325,
    "50/50" = C1G350,
    "75/25" = C1G375
  ),
  "Collagen IFibronectin" = list(
    "25/75" = C1FN25,
    "50/50" = C1FN50,
    "75/25" = C1FN75
  ),
  "Collagen IV" = list(
    "100" = C4100
  ),
  "Collagen IVLaminin" = list(
    "25/75" = C4LN25,
    "50/50" = C4LN50,
    "75/25" = C4LN75
  ),
  "Collagen IVTenascin C" = list(
    "25/75" = C4TC25,
    "50/50" = C4TC50,
    "75/25" = C4TC75
  ),
  "Collagen IVHyaluronic Acid" = list(
    "25/75" = C4HA25,
    "50/50" = C4HA50,
    "75/25" = C4HA75
  ),
  "Collagen IVOsteopontin" = list(
    "25/75" = C4OPN25,
    "50/50" = C4OPN50,
    "75/25" = C4OPN75
  ),
  "Collagen IVDecorin" = list(
    "25/75" = C4DN25,
    "50/50" = C4DN50,
    "75/25" = C4DN75
  ),
  
  "Collagen IVGalectin 3" = list(
    "25/75" = C4G325,
    "50/50" = C4G350,
    "75/25" = C4G375
  ),
  
  "Collagen IVFibronectin" = list(
    "25/75" = C4FN25,
    "50/50" = C4FN50,
    "75/25" = C4FN75
  ),
  
  "LamininTenascin C" = list(
    "25/75" = LNTC25,
    "50/50" = LNTC50,
    "75/25" = LNTC75
  ),
  
  "LamininHyaluronic Acid" = list(
    "25/75" = LNHA25,
    "50/50" = LNHA50,
    "75/25" = LNHA75
  ),
  
  "LamininOsteopontin" = list(
    "25/75" = LNOPN25,
    "50/50" = LNOPN50,
    "75/25" = LNOPN75
  ),
  
  "LamininDecorin" = list(
    "25/75" = LNDN25,
    "50/50" = LNDN50,
    "75/25" = LNDN75
  ),
  
  "LamininGalectin 3" = list(
    "25/75" = LNG325,
    "50/50" = LNG350,
    "75/25" = LNG375
  ),
  
  "LamininFibronectin" = list(
    "25/75" = LNFN25,
    "50/50" = LNFN50,
    "75/25" = LNFN75
  ),
  
  "Tenascin CHyaluronic Acid" = list(
    "25/75" = TCHA25,
    "50/50" = TCHA50,
    "75/25" = TCHA75
  ),
  
  "Tenascin COsteopontin" = list(
    "25/75" = TCOPN25,
    "50/50" = TCOPN50,
    "75/25" = TCOPN75
  ),
  "Tenascin CDecorin" = list(
    "25/75" = TCDN25,
    "50/50" = TCDN50,
    "75/25" = TCDN75
  ),
  "Tenascin CGalectin 3" = list(
    "25/75" = TCG325,
    "50/50" = TCG350,
    "75/25" = TCG375
  ),
  "Tenascin CFibronectin" = list(
    "25/75" = TCFN25,
    "50/50" = TCFN50,
    "75/25" = TCFN75
  ),
  "Hyaluronic AcidOsteopontin" = list(
    "25/75" = HAOPN25,
    "50/50" = HAOPN50,
    "75/25" = HAOPN75
  ),
  "Hyaluronic AcidDecorin" = list(
    "25/75" = HADN25,
    "50/50" = HADN50,
    "75/25" = HADN75
  ),
  "Hyaluronic AcidGalectin 3" = list(
    "25/75" = HAG325,
    "50/50" = HAG350,
    "75/25" = HAG375
  ),
  "Hyaluronic AcidFibronectin" = list(
    "25/75" = HAFN25,
    "50/50" = HAFN50,
    "75/25" = HAFN75
  ),
  "OsteopontinDecorin" = list(
    "25/75" = OPNDN25,
    "50/50" = OPNDN50,
    "75/25" = OPNDN75
  ),
  "OsteopontinGalectin 3" = list(
    "25/75" = OPNG325,
    "50/50" = OPNG350,
    "75/25" = OPNG375
  ),
  "OsteopontinFibronectin" = list(
    "25/75" = OPNFN25,
    "50/50" = OPNFN50,
    "75/25" = OPNFN75
  ),
  "DecorinGalectin 3" = list(
    "25/75" = DNG325,
    "50/50" = DNG350,
    "75/25" = DNG375
  ),
  "DecorinFibronectin" = list(
    "25/75" = DNFN25,
    "50/50" = DNFN50,
    "75/25" = DNFN75
  ),
  "Galectin 3Fibronectin" = list(
    "25/75" = G3FN25,
    "50/50" = G3FN50,
    "75/25" = G3FN75
  ),
  "Laminin" = list(
    "100" = LN100
  ),
  "Tenascin C" = list(
    "100" = TC100
  ),
  "Hyaluronic Acid" = list(
    "100" = HA100
  ),
  "Osteopontin" = list(
    "100" = OPN100
  ),
  "Decorin" = list(
    "100" = DN100
  ),
  "Galectin 3" = list(
    "100" = G3100
  ),
  "Fibronectin" = list(
    "100" = FN100
  )
  )

for (i in 1: nrow(combined_dsRatio)) {
  metadata_ecms <- combined_dsRatio[i,"Metadata_ECMs"]
  metadata_ratio <- combined_dsRatio[i,"Metadata_Ratio"]
  metadata_ecms <- unlist(metadata_ecms)
  metadata_ratio <- unlist(metadata_ratio)
  current_test_conditions <- list()
  current_test_conditions <- experimental_conditions[[metadata_ecms]][[metadata_ratio]]
  
  current_C1 <- current_test_conditions[1]
  current_C4 <- current_test_conditions[2]
  current_LN <- current_test_conditions[3]
  current_TC <- current_test_conditions[4]
  current_HA <- current_test_conditions[5]
  current_OPN <- current_test_conditions[6]
  current_DN <- current_test_conditions[7]
  current_G3 <- current_test_conditions[8]
  current_FN <- current_test_conditions[9]
  
  combined_dsRatio[i, "CollagenI"] <- current_C1
  combined_dsRatio[i, "CollagenIV"] <- current_C4
  combined_dsRatio[i, "Laminin"] <- current_LN
  combined_dsRatio[i, "TenascinC"] <- current_TC
  combined_dsRatio[i, "Hyaluronic_Acid"] <- current_HA
  combined_dsRatio[i, "Osteopontin"] <- current_OPN
  combined_dsRatio[i, "Decorin"] <- current_DN
  combined_dsRatio[i, "Galectin3"] <- current_G3
  combined_dsRatio[i, "Fibronectin"] <- current_FN
}

```


## Adding Replicates
```{r}
withrep<-combined_dsRatio%>%group_by(Metadata_Experiment, Metadata_Block, Metadata_Slide)%>%
  summarize(count = n(), .groups = "drop"
            )

 withrep$Replicate <-rep(c(1,2,3), times = 8)
 withrep <- withrep[, -4]

 dswithrep <- merge(combined_dsRatio, withrep) 
 
 dswithrep <- dswithrep %>% mutate(Conditions = paste(dswithrep$Abb_ECM, dswithrep$Metadata_Ratio))
```
