---
title: 'Classification'
author: 'Dataset res.PCA'
output:
  html_document: default
---
.

- - -

```{r, echo = FALSE}
library(FactoMineR)
load('C:/Users/SantaLucia/Documents/git/DREMT 12-18 Modeling Analysis/PCA2-17/Workspace.RData')
```

```{r, echo = FALSE, fig.align = 'center', fig.height = 5.5, fig.width = 5.5}
drawn <-
c("95", "51", "209")
par(mar = c(4.1, 4.1, 1.1, 2.1))
plot.HCPC(res, choice = 'tree', title = '')
```

**Figure 1.1 - Hierarchical tree.**

The classification made on individuals reveals 4 clusters.


```{r, echo = FALSE, fig.align = 'center', fig.height = 5.5, fig.width = 5.5}
par(mar = c(4.1, 4.1, 1.1, 2.1))
plot.HCPC(res, choice = 'map', draw.tree = FALSE, title = '')
```

**Figure 1.2 - Ascending Hierarchical Classification of the individuals.**

The **cluster 1** is made of individuals such as *209*. This group is characterized by :

- high values for the variables *Adhesion*, *Proliferation_DMSO*, *CollagenIV*, *Proliferation_10.uM* and *CollagenI* (variables are sorted from the strongest).
- low values for the variables *Mean_PXR*, *Mean_Vimentin*, *Survival_20.uM*, *Mean_Ecad* and *Survival_10.uM* (variables are sorted from the weakest).

The **cluster 2** is made of individuals sharing :

- high values for the variables *Mean_Vimentin*, *Proliferation_DMSO*, *Mean_PXR* and *Fibronectin* (variables are sorted from the strongest).
- low values for the variables *Proliferation_20.uM*, *Adhesion*, *Survival_20.uM*, *Survival_10.uM*, *CollagenIV* and *Proliferation_10.uM* (variables are sorted from the weakest).

The **cluster 3** is made of individuals such as *51* and *95*. This group is characterized by :

- high values for the variables *Survival_20.uM* and *Survival_10.uM* (variables are sorted from the strongest).
- low values for the variables *Proliferation_DMSO*, *Proliferation_10.uM*, *Mean_PXR*, *Mean_Ecad*, *Mean_Vimentin* and *Adhesion* (variables are sorted from the weakest).

The **cluster 4** is made of individuals sharing :

- high values for the variables *Mean_PXR*, *Mean_Ecad*, *Proliferation_20.uM*, *Survival_20.uM*, *Mean_Vimentin*, *Proliferation_10.uM* and *Laminin* (variables are sorted from the strongest).
- low values for the variables *Proliferation_DMSO*, *Adhesion* and *Galectin3* (variables are sorted from the weakest).


```{r, echo = FALSE, fig.align = 'center', fig.height = 5.5, fig.width = 5.5}
par(mar = c(4.1, 4.1, 1.1, 2.1))
plot.HCPC(res, choice = '3D.map', ind.names=FALSE, title = '')
```

**Figure 1.3 - Hierarchical tree on the factorial map.**

The hierarchical tree can be drawn on the factorial map with the individuals colored according to their clusters.


