---
title: "PCA2-17"
output: html_document
date: "2025-02-18"
---
## Library Loading
```{r}
library(FactoMineR)
library(Factoshiny)
library(ggplot2)
library(ggprism)
library(tidyr)
library(plyr)
library(dplyr)
```

### EdU and Survival
```{r}
## The EdU and Survival info is still at the ds_e_pheno, needs to be summarized together prior to merging with DREMT info
EdUtoadd217 <- FOC[, c("Metadata_Experiment", "Metadata_Stiffness", "Metadata_Treatment", "Metadata_Ratio", "Metadata_ECMs", "Mean_Percent_Positive")]

colnames(EdUtoadd217) <- c("Metadata_Experiment", "Metadata_Stiffness", "Metadata_Treatment", "Metadata_Ratio", "Metadata_ECMs", "Percent_Positive_EdU")

## Summarize to ds_pheno level
EdUreduced217 <- EdUtoadd217 %>% dplyr::group_by(Metadata_Treatment, Metadata_Stiffness, Metadata_Ratio, Metadata_ECMs) %>% dplyr::summarize(Proliferation = mean(Percent_Positive_EdU, na.rm = TRUE))

EdUreduced217 <- pivot_wider(EdUreduced217, names_from = Metadata_Treatment, values_from = Proliferation, names_prefix = "Proliferation_")

## Fold Change
FoldChange217 <- FOC[, c("Metadata_Experiment", "Metadata_Stiffness", "Metadata_Treatment", "Metadata_Ratio", "Metadata_ECMs", "FOC")]

## Summarize to ds_pheno level
FoldChange217 <- FoldChange217 %>% dplyr::group_by(Metadata_Stiffness, Metadata_Treatment, Metadata_Ratio, Metadata_ECMs) %>% dplyr::summarize(Survival = mean(FOC, na.rm = TRUE))

FoldChange217 <- subset(FoldChange217, Metadata_Treatment != "DMSO")

FoldChange217 <- pivot_wider(FoldChange217, names_from = Metadata_Treatment, values_from = Survival, names_prefix = "Survival_")

#FoldChange217 <- subset(FoldChange, select = -c(Metadata_Treatment))

## Join together to add

EdUSurv <- join(EdUreduced217, FoldChange217)

Ratios <- FOC %>% distinct(Metadata_ECMs, Metadata_Ratio, CollagenI, CollagenIV, Hyaluronic_Acid, TenascinC, Galectin3, Decorin, Fibronectin, Osteopontin, Laminin)

EdUSurv <- join(EdUSurv, Ratios)
```

### Formatting DREMT Info
```{r}
DREMTtoadd217 <- DMSOdsewithrep[,c("Metadata_Stiffness", "Metadata_Ratio", "Abb_ECM", "Metadata_ECMs","Mean_Green_Norm", "Mean_Orange_Norm", "Mean_Red_Norm", "Mean_Nuclei")]

## summarize to ds_pheno level
DREMTreduced217 <- DREMTtoadd217 %>% dplyr::group_by(Metadata_Stiffness, Metadata_Ratio, Metadata_ECMs, Abb_ECM) %>% 
 dplyr:: summarize(Mean_Vimentin = mean(Mean_Orange_Norm),
            Mean_Ecad = mean(Mean_Red_Norm),
            Mean_PXR = mean(Mean_Green_Norm),
            Adhesion = mean(Mean_Nuclei))
```

### Putting it All Together
```{r}
DMSOforPCA217 <- join(DREMTreduced217, EdUSurv)

#DMSOforPCA217  <- DMSOforPCA217[,-3]
```


## PCA Running
Adding Survival and EdU for All Treatments
```{r}
PCAshiny(DMSOforPCA217)
```

## Graphing the Clusters
```{r}
PCAClusters217 <- res$call$X

ggplot(PCAClusters217,aes(x = Dim.1,
                       y = Dim.2,
                       color = clust
)) + 
  geom_point(position = "jitter",size = 3)+
 # xlim(-2,6)+
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = 0)+
  theme_prism()+
  scale_color_manual(values=c("#003f5c", "#7a5195", "#ef5675", "#ffa600"), name = "Cluster")+
  # theme(
  #   axis.title.x = element_text(size= 30),
  #       axis.text.x = element_text(angle = 0, size= 20),
  #       axis.title.y = element_text(size= 30),
  #       axis.text.y = element_text(size= 15),
  #       strip.text =  element_text(size = 30),
  #       panel.background = element_blank(),
  #       legend.key.size = unit(2, 'cm'),
  #       legend.title = element_text(size = 30),
  #       legend.text = element_text(size = 30),
  # )+
  xlab("Dim. 1 - 31.30%") +
  ylab("Dim. 2 - 20.84%")
 
ggsave(filename = "PCAClusters2-17.png")

ggplot(PCAClusters217,aes(x = Dim.2,
                       y = Dim.3,
                       color = clust
)) + 
  geom_point(position = "jitter",size = 3)+
 # xlim(-2,6)+
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = 0)+
  theme_prism()+
  scale_color_manual(values=c("#003f5c", "#7a5195", "#ef5675", "#ffa600"), name = "Cluster")+
  xlab("Dim. 2 - 20.84%") +
  ylab("Dim. 3 - 14.89%")
 
ggsave(filename = "PCAClusters2-17D23.png")

ggplot(PCAClusters217,aes(x = Dim.1,
                       y = Dim.3,
                       color = clust
)) + 
  geom_point(position = "jitter",size = 3)+
 # xlim(-2,6)+
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = 0)+
  theme_prism()+
  scale_color_manual(values=c("#003f5c", "#7a5195", "#ef5675", "#ffa600"), name = "Cluster")+
  xlab("Dim. 1 - 31.30%") +
  ylab("Dim. 3 - 14.89%")
 
ggsave(filename = "PCAClusters2-17D13.png")
```


```{r}
datacluster217 <- res$data.clust
  
datacluster217 <- mutate(datacluster217, Individual = row.names(datacluster217))

PCAStiff217 <- mutate(PCAClusters217, Individual = row.names(PCAClusters217))

PCAStiff217<- merge(datacluster217, PCAClusters217)
```


NEED TO RUN - Find the Assignments with Cluster....
```{r}
ggplot(PCAStiff217,aes(x = Dim.1,
                       y = Dim.2,
                       color = Metadata_Stiffness
)) + 
  geom_point(position = "jitter",size = 3)+
  # xlim(-2,6)+
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = 0)+
  theme_prism()+
  scale_color_manual(values = c("#db6d22", "#2100bb"))+
  # theme(
  #   axis.title.x = element_text(size= 30),
  #       axis.text.x = element_text(angle = 0, size= 20),
  #       axis.title.y = element_text(size= 30),
  #       axis.text.y = element_text(size= 15),
  #       strip.text =  element_text(size = 30),
  #       panel.background = element_blank(),
  #       legend.key.size = unit(2, 'cm'),
  #       legend.title = element_text(size = 30),
  #       legend.text = element_text(size = 30),
  # )+
xlab("Dim. 1 - 31.30%") +
  ylab("Dim. 2 - 20.84%")

ggsave(filename = "StiffPCA.png")
```

## Variable Descriptions
```{r}
res$desc.var

res$desc.axes
```

## Identifying Individuals
```{r}
datawithcluster217 <- res$data.clust

MetatoAbbECMs <- unique(DMSOdsewithrep[c("Metadata_ECMs", "Abb_ECM")])

datawithcluster217 <- left_join(datawithcluster217, MetatoAbbECMs)

res$desc.ind
```


## Cluster Heatmaps
Import Metadata_ECMsbackward.csv and Metadata_ECMsforward.csv before running
```{r}
DC_125 <- subset(datawithcluster217, Metadata_Stiffness == "1kPa" & Metadata_Ratio %in% c("Metadata_Ratio_25/75", "Metadata_Ratio_100"))
DC_150 <- subset(datawithcluster217, Metadata_Stiffness == "1kPa" & Metadata_Ratio %in% c("Metadata_Ratio_50/50", "Metadata_Ratio_100"))
DC_175 <- subset(datawithcluster217, Metadata_Stiffness == "1kPa" & Metadata_Ratio %in% c("Metadata_Ratio_75/25", "Metadata_Ratio_100"))

DC_2525 <- subset(datawithcluster217, Metadata_Stiffness == "25kPa" & Metadata_Ratio %in% c("Metadata_Ratio_25/75", "Metadata_Ratio_100"))
DC_2550 <- subset(datawithcluster217, Metadata_Stiffness == "25kPa" & Metadata_Ratio %in% c("Metadata_Ratio_50/50", "Metadata_Ratio_100"))
DC_2575 <- subset(datawithcluster217, Metadata_Stiffness == "25kPa" & Metadata_Ratio %in% c("Metadata_Ratio_75/25", "Metadata_Ratio_100"))

DC_125for <- left_join(DC_125, Metadata_ECMsforward)
DC_150for <- left_join(DC_150, Metadata_ECMsforward)
DC_175for <- left_join(DC_175, Metadata_ECMsforward)

DC_2525for <- left_join(DC_2525, Metadata_ECMsforward)
DC_2550for <- left_join(DC_2550, Metadata_ECMsforward)
DC_2575for <- left_join(DC_2575, Metadata_ECMsforward)
  
DC_125back <- left_join(DC_125, Metadata_ECMsbackward)
DC_150back <- left_join(DC_150, Metadata_ECMsbackward)
DC_175back <- left_join(DC_175, Metadata_ECMsbackward)

DC_2525back <- left_join(DC_2525, Metadata_ECMsbackward)
DC_2550back <- left_join(DC_2550, Metadata_ECMsbackward)
DC_2575back <- left_join(DC_2575, Metadata_ECMsbackward)
  
DC_125 <- rbind(DC_125for,DC_125back)
DC_150 <- rbind(DC_150for,DC_150back)
DC_175 <- rbind(DC_175for,DC_175back)

DC_2525 <- rbind(DC_2525for,DC_2525back)
DC_2550 <- rbind(DC_2550for,DC_2550back)
DC_2575 <- rbind(DC_2575for,DC_2575back)
```

### Plotting
```{r}
library(viridis)
library(ggpubr)

a <- ggplot(DC_125 , aes(x = ECM1, y = ECM2, fill = clust))+
  geom_tile()+
  coord_fixed()+ 
  theme_prism()+ 
  ggtitle("1 kPa 25:75")+
  scale_fill_manual(values=c("#003f5c", "#7a5195", "#ef5675", "#ffa600"), name = "Cluster")+
  theme(axis.text.x = element_text( size = 25),
        axis.title.x = element_text(size = 25),
        axis.text.y = element_text(size = 25), 
        axis.title.y = element_text(size = 25),
        legend.key.height = unit(1, "in"),
        legend.text = element_text(size = 25),
        plot.title = element_text(size =30),
        panel.background = element_blank(),
        strip.text = element_text(size = 25),
        panel.border = element_rect(colour = "black", fill=NA, size=1))

b <- ggplot(DC_150, aes(x = ECM1, y = ECM2, fill = clust))+
  geom_tile()+
  coord_fixed()+ 
  theme_prism()+ 
  scale_fill_manual(values=c("#003f5c", "#7a5195", "#ef5675", "#ffa600"), name = "Cluster")+
  ggtitle("1 kPa 50:50")+
  theme(axis.text.x = element_text( size = 25),
        axis.title.x = element_text(size = 25),
        axis.text.y = element_text(size = 25), 
        axis.title.y = element_text(size = 25),
        legend.key.height = unit(1, "in"),
        legend.text = element_text(size = 25),
        plot.title = element_text(size =30),
        panel.background = element_blank(),
        strip.text = element_text(size = 25),
        panel.border = element_rect(colour = "black", fill=NA, size=1))

c <- ggplot(DC_175, aes(x = ECM1, y = ECM2, fill = clust))+
  geom_tile()+
  coord_fixed()+ 
  theme_prism()+ 
  scale_fill_manual(values=c("#003f5c", "#7a5195", "#ef5675", "#ffa600"), name = "Cluster")+
  ggtitle("1 kPa 75:25")+
  theme(axis.text.x = element_text( size = 25),
        axis.title.x = element_text(size = 25),
        axis.text.y = element_text(size = 25), 
        axis.title.y = element_text(size = 25),
        legend.key.height = unit(1, "in"),
        legend.text = element_text(size = 25),
        plot.title = element_text(size =30),
        panel.background = element_blank(),
        strip.text = element_text(size = 25),
        panel.border = element_rect(colour = "black", fill=NA, size=1))

d <- ggplot(DC_2525, aes(x = ECM1, y = ECM2, fill = clust))+
  geom_tile()+
  coord_fixed()+ 
  theme_prism()+ 
  scale_fill_manual(values=c("#003f5c", "#7a5195", "#ef5675", "#ffa600"), name = "Cluster")+
  ggtitle("25 kPa 25:75")+
  theme(axis.text.x = element_text( size = 25),
        axis.title.x = element_text(size = 25),
        axis.text.y = element_text(size = 25), 
        axis.title.y = element_text(size = 25),
        legend.key.height = unit(1, "in"),
        legend.text = element_text(size = 25),
        plot.title = element_text(size =30),
        panel.background = element_blank(),
        strip.text = element_text(size = 25),
        panel.border = element_rect(colour = "black", fill=NA, size=1))

e <- ggplot(DC_2550, aes(x = ECM1, y = ECM2, fill = clust))+
  geom_tile()+
  coord_fixed()+ 
  theme_prism()+ 
  scale_fill_manual(values=c("#003f5c", "#7a5195", "#ef5675", "#ffa600"), name = "Cluster")+
  ggtitle("25 kPa 50:50")+
  theme(axis.text.x = element_text( size = 25),
        axis.title.x = element_text(size = 25),
        axis.text.y = element_text(size = 25), 
        axis.title.y = element_text(size = 25),
        legend.key.height = unit(1, "in"),
        legend.text = element_text(size = 25),
        plot.title = element_text(size =30),
        panel.background = element_blank(),
        strip.text = element_text(size = 25),
        panel.border = element_rect(colour = "black", fill=NA, size=1))

f <- ggplot(DC_2575, aes(x = ECM1, y = ECM2, fill = clust))+
  geom_tile()+
  coord_fixed()+ 
  theme_prism()+ 
  scale_fill_manual(values=c("#003f5c", "#7a5195", "#ef5675", "#ffa600"), name = "Cluster")+
  ggtitle("25 kPa 75:25")+
  theme(axis.text.x = element_text( size = 25),
        axis.title.x = element_text(size = 25),
        axis.text.y = element_text(size = 25), 
        axis.title.y = element_text(size = 25),
        legend.key.height = unit(1, "in"),
        legend.text = element_text(size = 25),
        plot.title = element_text(size =30),
        panel.background = element_blank(),
        strip.text = element_text(size = 25),
        panel.border = element_rect(colour = "black", fill=NA, size=1))

Clust1grid <- ggarrange(a,b,c, ncol = 3, nrow =1)
Clust25grid <- ggarrange(d,e,f, ncol = 3, nrow = 1)

ggsave(Clust1grid, filename = "Clust1kPa.png", width = 30, height = 10)
ggsave(Clust25grid, filename = "Clust25kPa.png", width = 30, height = 10)

```


